---
title: "table1_sl_outcomes"
author: "Drew Walker"
date: "9/13/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(table1)
library(haven)
library(sjPlot)
library(sjmisc)
library(sjlabelled)

```

```{r read-data}
sl_demo_raw <- read_csv("table1.csv")

sl_demo_raw$streetlight_evaluation_survey_complete <- as.factor(sl_demo_raw$streetlight_evaluation_survey_complete)
sl_demo_raw$yqolsf_complete <- as.factor(sl_demo_raw$yqolsf_complete)

sl_demo_raw$demographic_questionnaire_complete <- as.factor(sl_demo_raw$demographic_questionnaire_complete)

sl_demo_raw$gender <- as.factor(sl_demo_raw$gender)

sl_demo_raw$diagnosis <- as.factor(sl_demo_raw$diagnosis)

sl_demo_raw$ethnicity <- as.factor(sl_demo_raw$ethnicity)

sl_demo_raw$other_disease <- as.factor(sl_demo_raw$other_disease)

sl_demo_clean <- sl_demo_raw %>% 
  mutate(interview_requested = case_when(is.na(interview_request_name) ~ "No",
                                         TRUE ~ "Yes"),
         sl_outcomes_avg = (q1_control+q2_getalong_hosp+q3_getalong_fam+q4_easier_tasks+q6_roomhang_fun+q7_friends_roomhang+q8_talk_badday+q_32+q11_respect_all+q13_badday_there+q14_there_hang+q15_sl_friends+q16_hang_better+q17_eot_good+q18_imp_treat_event+q19_happy_mem)/16,
         sl_outcomes_st = scale(sl_outcomes_avg),
         sl_outcomes_sum = (q1_control+q2_getalong_hosp+q3_getalong_fam+q4_easier_tasks+q6_roomhang_fun+q7_friends_roomhang+q8_talk_badday+q_32+q11_respect_all+q13_badday_there+q14_there_hang+q15_sl_friends+q16_hang_better+q17_eot_good+q18_imp_treat_event+q19_happy_mem),
         sl_friends = (q8_talk_badday+q_32+q15_sl_friends+q7_friends_roomhang+q18_imp_treat_event+q14_there_hang+q13_badday_there)/7,
         sl_friends_st = scale(sl_friends),
         sl_friends_sum = (q8_talk_badday+q_32+q15_sl_friends+q7_friends_roomhang+q18_imp_treat_event+q14_there_hang+q13_badday_there),
         sl_family = (q2_getalong_hosp+q4_easier_tasks+q3_getalong_fam+q1_control+q17_eot_good)/5,
         sl_family_st = scale(sl_family),
         sl_family_sum = (q2_getalong_hosp+q4_easier_tasks+q3_getalong_fam+q1_control+q17_eot_good),
         sl_diversion = (q19_happy_mem+q11_respect_all+q6_roomhang_fun+q16_hang_better)/4,
         sl_diversion_st = scale(sl_diversion),
         sl_diversion_sum = (q19_happy_mem+q11_respect_all+q6_roomhang_fun+q16_hang_better),
         t_r07 = (((r07 - 1)/2)*100),
         t_r08 = (((r08 - 1)/2)*100),
         t_r11 = (((r11 - 1)/2)*100),
         t_r16 = (((r16 - 1)/2)*100),
         t_r19 = (((r19 - 1)/2)*100),
         t_r20 = (((r20 - 1)/2)*100),
         t_r24 = (((r24 - 1)/2)*100),
         t_r26 = (((r27 - 1)/2)*100),
         t_r27 = (((r27 - 1)/2)*100),
         t_r32 = (((r32 - 1)/2)*100),
         t_r36 = (((r36 - 1)/2)*100),
         t_r38 = (((r38 - 1)/2)*100),
         t_r13 = (((r13 - 1)/2)*100),
         t_r35 = (((r35 - 1)/2)*100),
         t_r37 = (((r37 - 1)/2)*100),
         t_r34 = (((r34 - 1)/2)*100),
         yqol_outcomes_avg = (t_r07+t_r08+t_r11+t_r16+t_r19+t_r20+t_r24+t_r26+t_r27+t_r32+t_r36+t_r38+t_r13+t_r35+t_r37+t_r34)/16,
         yqol_outcomes_st = scale(yqol_outcomes_avg),
         yqol_self_and_family = (t_r07+t_r08+t_r16+t_r19+t_r20)/5,
         yqol_self_and_family_st = scale(yqol_self_and_family),
         yqol_env_and_relationships = (t_r24+t_r26+t_r27+t_r32+t_r34+t_r35)/6,
         yqol_env_and_relationships_st = scale(yqol_env_and_relationships))
           

# ones not applicable to all
#q24_slmemb_ill, q25_outpat_trans_talk, q26_outpattrans_friend, q27_adulttrans_talk, q28_adulttrans_friend, q30_cf_yearbook, q31_experience
           
#q21_lounge_fun,q23_lounge_age 
sl_demo_clean$interview_requested <- as.factor(sl_demo_clean$interview_requested)

sl_demo_clean$school___1 <- as.factor(sl_demo_clean$school___1)
sl_demo_clean$school___2 <- as.factor(sl_demo_clean$school___2)
sl_demo_clean$school___3 <- as.factor(sl_demo_clean$school___3)
sl_demo_clean$school___4 <- as.factor(sl_demo_clean$school___4)
sl_demo_clean$school___5 <- as.factor(sl_demo_clean$school___5)
sl_demo_clean$school___6 <- as.factor(sl_demo_clean$school___6)
sl_demo_clean$school___7 <- as.factor(sl_demo_clean$school___7)
sl_demo_clean$school___8 <- as.factor(sl_demo_clean$school___8)
sl_demo_clean$school___9 <- as.factor(sl_demo_clean$school___9)
sl_demo_clean$hospital_now <- as.factor(sl_demo_clean$hospital_now)


table1(~streetlight_evaluation_survey_complete + yqolsf_complete + demographic_questionnaire_complete + gender + diagnosis + ethnicity + other_disease + interview_requested + age + yqol_outcomes_avg + yqol_self_and_family + yqol_env_and_relationships + +sl_outcomes_avg + school___1 +school___2+ school___3+ school___4+school___5+ school___6+ school___7+ school___8+ school___9 + hospital_now + q21_lounge_fun + q22_lounge_friends + q23_lounge_age + q24_slmemb_ill + q25_outpat_trans_talk + q26_outpattrans_friend + q27_adulttrans_talk + q28_adulttrans_friend + q30_cf_yearbook + q31_experience + exp_other, data = sl_demo_clean )

open_ended_survey_df <- sl_demo_clean %>% 
  filter(!is.na(exp_other)|!is.na(q31_experience)) %>% 
  mutate(completed_other = !is.na(exp_other),
         completed_helpful = !is.na(q31_experience)) 
table1(~completed_other + completed_helpful | interview_requested, data = open_ended_survey_df)
  
```
# Sensitivity/logistic regressions for qual of life and SL eval outcome scores
* if ppl selected to interview-- no significant relationship
* if ppl were in hospital -- no sig relationship 
* differences across disease populations  -- no sig relationship
* association between scores  --

```{r regressions}
sl_demo_clean$hospital_now
model_interview_yqol <- lm(yqol_outcomes_avg~interview_requested, data = sl_demo_clean)
summary(model_interview_yqol)

model_interview_sl <- lm(sl_outcomes_avg~interview_requested, data= sl_demo_clean)
summary(model_interview_sl)

# No significant associations between requested interview and YQOL/SL 

model_hospital_yqol <- lm(yqol_outcomes_avg~hospital_now, data = sl_demo_clean)
summary(model_hospital_yqol)

model_hospital_sl <- lm(sl_outcomes_avg~hospital_now, data= sl_demo_clean)
summary(model_hospital_sl)

# No significant associaitons here whether hospitalized/not- may point to need to continue services outpatient related to QOL 

model_diagnosis_yqol <- lm(yqol_outcomes_avg~diagnosis, data = sl_demo_clean)
summary(model_diagnosis_yqol)

model_diagnosis_sl <- lm(sl_outcomes_avg~diagnosis, data= sl_demo_clean)
summary(model_diagnosis_sl)

# No significant associations here

model_sl_and_yqol <- lm(yqol_outcomes_avg ~ sl_outcomes_avg, data = sl_demo_clean)
summary(model_sl_and_yqol)

# none found here

## Add age 
model_age_yqol <- lm(yqol_outcomes_avg~age, data = sl_demo_clean)
summary(model_age_yqol)

model_age_sl <- lm(sl_outcomes_avg~age, data= sl_demo_clean)
summary(model_age_sl)

# and gender 

model_gender_yqol <- lm(yqol_outcomes_avg~gender, data = sl_demo_clean)
summary(model_gender_yqol)

model_gender_sl <- lm(sl_outcomes_avg~gender, data= sl_demo_clean)
summary(model_gender_sl)

```
# Factor models

* Using EFA factors as regression predictors/outcomes 

```{r sl-factors-and-yqol}

#yqol_friends, yqol_family ,yqol_meaning 
#model_friends_factor <- lm(yqol_friends~sl_outcomes_avg, data= sl_demo_clean)
#summary(model_friends_factor)
#
#model_family_factor <- lm(yqol_family~sl_outcomes_avg, data= sl_demo_clean)
#summary(model_family_factor)
#
#model_meaning_factor <- lm(yqol_meaning~sl_outcomes_avg, data= sl_demo_clean)
#summary(model_meaning_factor)
#

model_yqol_sl_outcomes <- lm(yqol_outcomes_st~sl_outcomes_st, data= sl_demo_clean)
summary(model_yqol_sl_outcomes)
confint(model_yqol_sl_outcomes)

model_yqol_sl_friend <- lm(yqol_outcomes_st~sl_friends_st, data= sl_demo_clean)
summary(model_yqol_sl_friend)
confint(model_yqol_sl_friend)

## Specific SL Factors sl_friends, sl_family, sl_diversion

model_yqol_sl_factors <- lm(yqol_outcomes_st~sl_friends_st + sl_family_st + sl_diversion_st, data= sl_demo_clean)
summary(model_yqol_sl_factors)
confint(model_yqol_sl_factors)

model_friends_sl_factors <- lm(yqol_env_and_relationships_st~sl_friends_st, data= sl_demo_clean)
summary(model_friends_sl_factors)
confint(model_friends_sl_factors)


model_friends_sl_diversion <- lm(yqol_env_and_relationships_st~sl_diversion_st, data = sl_demo_clean)
summary(model_friends_sl_diversion)
confint(model_friends_sl_diversion)

model_friends_sl_family <- lm(yqol_env_and_relationships_st~sl_family, data = sl_demo_clean)
summary(model_friends_sl_family)
confint(model_friends_sl_family)


model_friends_sl_outcomes_avg <- lm(yqol_env_and_relationships_st~sl_outcomes_st, data= sl_demo_clean)
summary(model_friends_sl_outcomes_avg)
confint(model_friends_sl_outcomes_avg)
## Redoing with sums as sensitivity check 



## Specific SL Factors sl_friends, sl_family, sl_diversion

```
# COmbined help and other wordcloud
```{r sl-descriptions-wordcloud-both}
library(tm)
library(wordcloud)
# sl_demo_clean$exp_other and sl_demo_clean$q31_experience 

exp_other <- as_tibble(sl_demo_clean$exp_other) %>% 
  drop_na() %>% 
  mutate(question = "other")
exp_helpful <- as_tibble(sl_demo_clean$q31_experience) %>% 
  drop_na() %>% 
  mutate(question = "helpful")

text <- bind_rows(exp_other,exp_helpful)

write_csv(text,"open_response_questions.csv")
text <- str_replace_all(text$value, fixed("narrative", ignore_case = TRUE), "")
docs <- Corpus(VectorSource(text))
docs <- docs %>% 
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, "streetlight")
dtm <- TermDocumentMatrix(docs) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
df <- data.frame(word = names(words),freq=words)
set.seed(4275) # for reproducibility 
wordcloud(words = df$word, freq = df$freq, min.freq = 2,           
          max.words=100, random.order=FALSE, rot.per=0.35,           
          colors=brewer.pal(8, "Dark2"))

```
# Helpful about sl experience wordcloud
```{r sl-descriptions-wordcloud-helpful}
library(tm)
library(wordcloud)
# sl_demo_clean$exp_other and sl_demo_clean$q31_experience 

text <- rbind(sl_demo_clean$q31_experience)
text <- str_replace_all(text, fixed("narrative", ignore_case = TRUE), "")
docs <- Corpus(VectorSource(text))
docs <- docs %>% 
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, "streetlight")
dtm <- TermDocumentMatrix(docs) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
df <- data.frame(word = names(words),freq=words)
set.seed(4275) # for reproducibility 
wordcloud(words = df$word, freq = df$freq, min.freq = 1,           
          max.words=100, random.order=FALSE, rot.per=0.35,           
          colors=brewer.pal(8, "Dark2"))

## bar chart
#count words
word_count <- df %>% 
  filter(word != "") %>% 
  count(word) %>% 
  arrange(-n) %>% 
  slice_max(n, n = 20)
mergeable_word_count <- df %>% 
  filter(word != "") %>% 
  count(word)
head(word_count,
     n = 20)
library(ggpubr)
word_count_bar <- ggplot(word_count, aes(x= fct_reorder(word,n),y = n, fill = word)) + 
          geom_col(show.legend = FALSE)+
  labs(x = "Word", y = "Top words Streetlight Helpful Questions")+
  coord_flip()+
  theme_pubclean()
word_count_bar
current_time <- Sys.time()
st <- format(current_time,"%Y-%m-%d_%H_%M")
library(here)
word_count_bar_filename <- paste0(here("helpful_word_count"),st,".png") 
ggsave(word_count_bar_filename)

```

# Other (anything else about) sl experience
```{r sl-descriptions-wordcloud-other}
library(tm)
library(wordcloud2)
# sl_demo_clean$exp_other and sl_demo_clean$q31_experience 

text <- rbind(sl_demo_clean$exp_other)
text <- str_replace_all(text, fixed("narrative", ignore_case = TRUE), "")
docs <- Corpus(VectorSource(text))
docs <- docs %>% 
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, "streetlight")
dtm <- TermDocumentMatrix(docs) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
df <- data.frame(word = names(words),freq=words)
set.seed(4275) # for reproducibility 
wordcloud(words = df$word, freq = df$freq, min.freq = 1,           
           max.words=50, random.order=FALSE, rot.per=0.35,colors=brewer.pal(8, "Dark2"))

word_count <- df %>% 
  filter(word != "") %>% 
  count(word) %>% 
  arrange(-n) %>% 
  slice_max(n, n = 20)
mergeable_word_count <- df %>% 
  filter(word != "") %>% 
  count(word)
head(word_count,
     n = 20)
library(ggpubr)
word_count_bar <- ggplot(word_count, aes(x= fct_reorder(word,n),y = n, fill = word)) + 
          geom_col(show.legend = FALSE)+
  labs(x = "Word", y = "Top words Streetlight Other Questions")+
  coord_flip()+
  theme_pubclean()
word_count_bar
current_time <- Sys.time()
st <- format(current_time,"%Y-%m-%d_%H_%M")
library(here)
word_count_bar_filename <- paste0(here("other_word_count"),st,".png") 
ggsave(word_count_bar_filename)


```

tf-idf other and helpful 
```{r tf-idf}
library(tidytext)
library(tidylo)
other <- as.tibble(sl_demo_clean$exp_other)
other <- other %>% 
  mutate(question = "other")
helpful <- as.tibble(sl_demo_clean$q31_experience)
helpful <- helpful %>% 
  mutate(question = "helpful")
combined <- rbind(other,helpful)
combined <- combined %>% 
  mutate(id = row_number())
stopwords <- stopwords::stopwords()
combined_id <- combined %>% 
  select(id, question)
combined_words <- combined %>% 
  unnest_tokens(word,value) %>% 
  left_join(combined_id,by = "id") 

combined_words <- combined_words %>% 
filter(!word %in% stopwords) %>% 
  group_by(question.x) %>% 
  count(word,sort = TRUE,.drop = TRUE) %>% 
  ungroup()
combined_tf_idf <- combined_words %>% 
  bind_tf_idf(word,question.x,n) %>% 
  arrange(desc(tf_idf))%>% 
  bind_log_odds(feature = word, set = question.x, n = n) %>% 
  mutate(lo_abs = abs(log_odds_weighted))
combined_tf_idf %>%
  group_by(question.x) %>%
  filter(lo_abs>1)%>%
  ungroup() %>%
  ggplot(aes(lo_abs, fct_reorder(word, lo_abs), fill = question.x)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~question.x, ncol = 2, scales = "free") +
  labs(x = "weighted log odds", y = NULL)+
  theme_classic()
```


# Revisions Models

* Want to assess SL scores as predictors for YQOL scores, broken by total avg score and factor specific scores

```{r revision-descriptives}
table1(~yqol_outcomes_avg + yqol_self_and_family + yqol_env_and_relationships +sl_outcomes_avg + sl_diversion + sl_family + sl_friends + sl_diversion, data = sl_demo_clean )
```

```{r revision-models}
table1(~yqol_outcomes_avg + yqol_self_and_family + yqol_env_and_relationships +sl_outcomes_avg + sl_diversion + sl_family + sl_friends + sl_diversion, data = sl_demo_clean )


#Covariates: age, gender, diagnosis
#Average SL x Average YQOL
model_yqol_sl_avg <- lm(yqol_outcomes_avg~sl_outcomes_avg +age + gender, data= sl_demo_clean)
summary(model_yqol_sl_avg)
confint(model_yqol_sl_avg)

# SL Friendships x yqol avg 

model_yqol_sl_friend <- lm(yqol_outcomes_avg~sl_friends + age + gender , data= sl_demo_clean)
summary(model_yqol_sl_friend)
confint(model_yqol_sl_friend)

##  sl_family x average

model_yqol_sl_family <- lm(yqol_outcomes_avg~sl_family + age + gender, data= sl_demo_clean)
summary(model_yqol_sl_family)
confint(model_yqol_sl_family)

# sl_diversion x average yqol
model_yqol_avg_sl_diversion <- lm(yqol_outcomes_avg~sl_diversion + age + gender, data= sl_demo_clean)
summary(model_yqol_avg_sl_diversion)
confint(model_yqol_avg_sl_diversion)



```

## Model tables 

### YQOL Average as Outcome
```{r model-revisions-table}
tab_model(model_yqol_sl_avg, model_yqol_sl_friend, model_yqol_sl_family,model_yqol_avg_sl_diversion, dv.labels = c("Streetlight Eval Avg","SL- Friendships and Support", " SL- Family and Coping", "SL- Diversion and Respect"), show.aic = TRUE, show.dev = TRUE)
```

### YQOL Env and Relationships as Outcome
```{r env-and-relrevision-models}
#Covariates: age, gender, diagnosis
#Average SL x Average YQOL
model_yqol_env_sl_avg <- lm(yqol_env_and_relationships~sl_outcomes_avg +age + gender, data= sl_demo_clean)
summary(model_yqol_env_sl_avg)
confint(model_yqol_env_sl_avg)

# SL Friendships x yqol env 

model_yqol_env_sl_friend <- lm(yqol_env_and_relationships~sl_friends + age + gender , data= sl_demo_clean)
summary(model_yqol_env_sl_friend)
confint(model_yqol_env_sl_friend)

##  sl_family x yqol env

model_yqol_env_sl_family <- lm(yqol_env_and_relationships~sl_family + age + gender, data= sl_demo_clean)
summary(model_yqol_env_sl_family)
confint(model_yqol_env_sl_family)

# sl_diversion x average yqol
model_yqol_env_sl_diversion <- lm(yqol_env_and_relationships~sl_diversion + age + gender, data= sl_demo_clean)
summary(model_yqol_env_sl_diversion)
confint(model_yqol_env_sl_diversion)

# Env and Relationships Outcome Table
tab_model(model_yqol_env_sl_avg, model_yqol_env_sl_friend, model_yqol_env_sl_family,model_yqol_env_sl_diversion, dv.labels = c("Streetlight Eval Avg","SL- Friendships and Support", " SL- Family and Coping", "SL- Diversion and Respect"), show.aic = TRUE, show.dev = TRUE)

```


### YQOL Self and Family as Outcome
```{r yqol-self-and-family-revision-models}
#Covariates: age, gender, diagnosis
#Average SL x Average YQOL
model_yqol_self_sl_avg <- lm(yqol_self_and_family~sl_outcomes_avg +age + gender, data= sl_demo_clean)
summary(model_yqol_self_sl_avg)
confint(model_yqol_self_sl_avg)

# SL Friendships x yqol env 

model_yqol_self_sl_friend <- lm(yqol_self_and_family~sl_friends + age + gender , data= sl_demo_clean)
summary(model_yqol_self_sl_friend)
confint(model_yqol_self_sl_friend)

##  sl_family x yqol env

model_yqol_self_sl_family <- lm(yqol_self_and_family~sl_family + age + gender, data= sl_demo_clean)
summary(model_yqol_self_sl_family)
confint(model_yqol_self_sl_family)

# sl_diversion x average yqol
model_yqol_self_sl_diversion <- lm(yqol_self_and_family~sl_diversion + age + gender, data= sl_demo_clean)
summary(model_yqol_self_sl_diversion)
confint(model_yqol_self_sl_diversion)

# yqol_self_and_family Outcome Table
tab_model(model_yqol_self_sl_avg, model_yqol_self_sl_friend,model_yqol_self_sl_family, model_yqol_self_sl_diversion, dv.labels = c("Streetlight Eval Avg","SL- Friendships and Support", " SL- Family and Coping", "SL- Diversion and Respect"), show.aic = TRUE, show.dev = TRUE)
```