---
title: "yqol_factor_analysis"
author: "Drew Walker"
date: "12/17/2021"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lavaan)
library(psych)
library(corrplot)
library("psych")
library(ggplot2)
library(GPArotation)
```

# Load data

```{r dataload}
yqolsf_scores <- read_csv("yqolsf_factor_ready.csv")
yqolsf_scores <- yqolsf_scores %>% 
  filter(yqolsf_complete == 2) %>% 
  select(-yqolsf_complete,-record_id)
describe(yqolsf_scores)


```

# EFA 

```{r efa}
datamatrix <- cor(yqolsf_scores, method = "pearson", use = "complete.obs")
corrplot(datamatrix, method="number")
KMO(r=cor(yqolsf_scores,method = "pearson", use = "complete.obs"))
cortest.bartlett(yqolsf_scores)
det(cor(yqolsf_scores,method = "pearson", use = "complete.obs"))

fafitfree <- fa(yqolsf_scores,nfactors = ncol(yqolsf_scores), rotate = "none")
n_factors <- length(fafitfree$e.values)
scree     <- data.frame(
  Factor_n =  as.factor(1:n_factors), 
  Eigenvalue = fafitfree$e.values)
ggplot(scree, aes(x = Factor_n, y = Eigenvalue, group = 1)) + 
  geom_point() + geom_line() +
  xlab("Number of factors") +
  ylab("Initial eigenvalue") +
  labs( title = "Scree Plot", 
        subtitle = "(Based on the unreduced correlation matrix)")

```

```{r efa-3-factor}
fa.none <- fa(r=yqolsf_scores,nfactors = 3, fm="mle", max.iter=200, rotate="oblimin") 
print(fa.none)

```


# CFA based on [@hoang2021]

## Factor 1: Belief in self and family

-   Q1 (r07): energy to do the things i want

-   Q2: (r_missing) Feel good about self

-   Q3: (r missing) I feel i am important to others

-   Q4 (r08): pleased with how i look

-   Q5 (r_missing) feel understood by family

-   Q6 (r_missing) feel i am getting along with my family

-   Q5 (r16): my family encourages me to do my best

-   Q6 (r19): i feel i am getting along with my parents or guardians

-   Q15 (r20): I feel my parents or guardians allow me to participate in
    important decisions which affect me

## Factor 2: Environment and relationships

-   Q8 (r24): I'm happy with the friends I have
-   Q9(r26): I feel i can take part in same activities as others my age
-   Q10(r27): People my age treat me with respect

Q12 (r32) I look forward to the future \* Q13 (r34): I feel safe when i
am at home \* Q14 (r35): Getting a good education

## NEW:

### Removed:

-   Q2: (r_missing) Feel good about self

-   Q3: (r missing) I feel i am important to others

-   Q5 (r_missing) feel understood by family

-   Q6 (r_missing) feel i am getting along with my family

-   Q11 (r_missing) Not in this questionnaire) Feel like my life is full
    of interesting things to do \*Q7 (r_missing) I feel alone in my life

### Added:

-   Q? Know how to get the information i need(r36), *Q? Enjoy learning
    new things (r37)* Q? Feel safe at school(r38) \*Q? (r11): i feel my
    life has meaning

<https://lavaan.ugent.be/tutorial/cfa.html>

```{r conf-factor-analysis}
str(yqolsf_scores)

#Belief in self and family



path <- ' self_and_family =~ r07 + r08 + r16 + r19 + r20 
          env_and_relationships =~ r24 + r26 + r27 + r32 + r34 + r35 '

model <- cfa(path, data= yqolsf_scores)
summary(model, fit.measures=TRUE)
```

